SPP-Perc: Peceptron Learning Based Enhanced Signature Path Prefetcher

### 2018-12-01 intro.tex
Including introduction illustration

@@

A delicate balance between coverage and accuracy is required for a prefetcher to maximize
its performance impact.  Prefetchers are generally designed with internal mechanisms to
monitor their accuracy, with throttling thresholds that can be tuned for either coverage 
or accuracy.  The more irregular an application's memory access pattern is, the more difficult
it is to accurately predict every access, so a prefetcher will have to be tuned more toward
coverage (and away from accuracy) in order to gain any benefit.  This may be especially dangerous
to do in the context of a multi-core processor, where overly aggressive prefetching in one core can
waste shared resources, such as last-level cache capacity, and off-chip bandwidth~\cite{Friendly}.

>>>>

\begin{figure}[t]
\includegraphics[width=\columnwidth]{Motivation}
\caption{Variation of IPC, Total Prefetches and Useful Prefetches}
\label{Fig:Motivation}
\end{figure}

@@

Figure~\ref{Fig:Motivation} illustrates the above scenario in a working manner.
Here we consider a state-of-the-art lookahead prefetcher -- SPP. We keep on 
re-tuning its thresholds, each time getting a variant with an increasing lookahead 
depth coverage. The figure depicts the behavior of the prefetcher variants running 
on the trace \textit{603.bwaves\_s-1740B}. The IPC, total number of prefetches 
suggested by the prefetcher (TOTAL\_PF) and the actual useful predictions (GOOD\_PF),
all have been normalized to the least aggressive version of the prefetcher. 
As the look-ahead depth of the prefetch suggestions increase, so do useful prefetches. 
But that comes at a cost of total prefetches inceasing at an even higher rate. This leads 
to cache pollution and bandwidth contention, as is clearly visible with the reduction in 
the IPC. Similar behaviour was observed in 12 other SPEC 2017 simpoints.

Therefore, a delicate balance between coverage and accuracy is required for a prefetcher to maximize
its performance impact.  Prefetchers are generally designed with internal mechanisms to
monitor their accuracy, with throttling thresholds that can be tuned for either coverage 
or accuracy.  The more irregular an application's memory access pattern is, the more difficult
it is to accurately predict every access, so a prefetcher will have to be tuned more toward
coverage (and away from accuracy) in order to gain any benefit.  This may be especially dangerous
to do in the context of a multi-core processor, where overly aggressive prefetching in one core can
waste shared resources, such as last-level cache capacity, and off-chip bandwidth~\cite{Friendly}.
